Intelligence and Age at First Intercourse: Cause or Confound?

### 2015-10-29 R/afidraftRnw.tex
updates

\documentclass[a4paper,man,apacite,natbib,12pt]{apa6}
%%%%%%%%%%%% Packages %%%%%%%%%%%%
%%% Formatting
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{verbatim}
\usepackage[yyyymmdd,hhmmss]{datetime}

@@

\authornote{This material is based upon work that has been supported by National Institute of Health under Grant No. (R01-HD065865) and the National Science Foundation Graduate Research Fellowship Program under Grant No. (DGE-1445197) and various means of institutional support from the following universities: University of British Columbia, University of Oklahoma \& Vanderbilt University.}

\begin{document}
\maketitle
%\linenumbers%\section{Introduction}\section{ }\vspace{-.8cm}
\input{content/introduction.txt}

@@

\section{Methods}\input{content/methods.txt}
<<setup, include=FALSE>>=
file_drive= "C:"
#file_drive="E:"
#Libraries

library(devtools);dev_mode(on=T)
library(effects)
library(ggplot2)
library(Hmisc)
library(knitr)
library(MplusAutomation)
library(NlsyLinks)
library(plyr);library(psych)
library(stargazer)
library(tables)
library(WrightMap)
library(xtable)
#install_github("LiveOak/NlsyLinks")
#install_github("ggplot2")#dev_mode(on=F) 
#install_github("harrelfe/Hmisc")
#Functions
####### FUNCTIONS #######
#source("https://raw.githubusercontent.com/smasongarrison/Functions/master/Mason_Functions.R")
source(paste(file_drive,"/Dropbox/Work/Templates/R/Functions/Mason_Functions.R",sep=""))

#OPtions
options(scipen=999)
options(digits=3)
options(width=60)
opts_chunk$set(fig.path='figure/beamer-',fig.align='center',fig.show='hold',size='footnotesize')

#Data_9
LinkedMDAN_discord_AFI_z_9 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_z_910811.csv",sep=""))
LinkedMDAN_discord_AFI_z_9$Gendermean<-as.factor(LinkedMDAN_discord_AFI_z_9$Gendermean)
LinkedMDAN_discord_AFI_g_9 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_girls_910811.csv",sep=""))
LinkedMDAN_discord_AFI_b_9 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_boys_910811.csv",sep=""))

#Models_9
data=LinkedMDAN_discord_AFI_z_9
model.meankids_9<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.int_9<-lm(Int_Mean ~ INTMOMmean, data = data)
model.meanmoms_9<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.diffkids_9 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms_9 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids_9 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean +INTMOMmean + Intdiff+  INTMOMdiff, data = data)
model.meanmomskids_9<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffmomsint_9 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff + Gendermean + INTMOMmean:Gendermean, data = data)
data=LinkedMDAN_discord_AFI_g_9

model.meankids.g_9<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.g_9<-lm(AFIKIDmean ~ INTMOMmean, data = data)
nested<-data
nested$Int_Mean[is.na(nested$Intdiff)] <- NA
model.diffkids.g_9<- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffkids.g.full_9 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = nested)
model.diffkids.g.nested_9 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean , data = nested)
anova_9<-anova(model.diffkids.g.nested_9,model.diffkids.g.full_9)
model.diffmoms.g_9<- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.g_9 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
model.meanmomskids.g_9<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
data=LinkedMDAN_discord_AFI_b_9
model.meankids.b_9<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.b_9<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.meanmomskids.b_9<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffkids.b_9 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms.b_9 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.b_9 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
@
<<setup_Data_10,include=FALSE>>=
#Data_10
LinkedMDAN_discord_AFI_z_10 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_z_1011912.csv",sep=""))
LinkedMDAN_discord_AFI_z_10$Gendermean<-as.factor(LinkedMDAN_discord_AFI_z_10$Gendermean)
LinkedMDAN_discord_AFI_g_10 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_girls_1011912.csv",sep=""))
LinkedMDAN_discord_AFI_b_10 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_boys_1011912.csv",sep=""))

#Models_10
data=LinkedMDAN_discord_AFI_z_10
model.meankids_10<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.int_10<-lm(Int_Mean ~ INTMOMmean, data = data)
model.meanmoms_10<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.diffkids_10 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms_10 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids_10 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean +INTMOMmean + Intdiff+  INTMOMdiff, data = data)
model.meanmomskids_10<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffmomsint_10 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff + Gendermean + INTMOMmean:Gendermean, data = data)
data=LinkedMDAN_discord_AFI_g_10

model.meankids.g_10<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.g_10<-lm(AFIKIDmean ~ INTMOMmean, data = data)
nested<-data
nested$Int_Mean[is.na(nested$Intdiff)] <- NA
model.diffkids.g_10<- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffkids.g.full_10 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = nested)
model.diffkids.g.nested_10 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean , data = nested)
anova_10<-anova(model.diffkids.g.nested_10,model.diffkids.g.full_10)
model.diffmoms.g_10<- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.g_10 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
model.meanmomskids.g_10<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
data=LinkedMDAN_discord_AFI_b_10
model.meankids.b_10<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.b_10<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.meanmomskids.b_10<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffkids.b_10 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms.b_10 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.b_10 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
@
<<setup_Data_11,include=FALSE>>=
#Data_11
LinkedMDAN_discord_AFI_z_11 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_z_11121013.csv",sep=""))
LinkedMDAN_discord_AFI_z_11$Gendermean<-as.factor(LinkedMDAN_discord_AFI_z_11$Gendermean)
LinkedMDAN_discord_AFI_g_11 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_girls_11121013.csv",sep=""))
LinkedMDAN_discord_AFI_b_11 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_boys_11121013.csv",sep=""))
data=LinkedMDAN_discord_AFI_z_11

#Models_11
model.meankids_11<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.int_11<-lm(Int_Mean ~ INTMOMmean, data = data)
model.meanmoms_11<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.diffkids_11 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms_11 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids_11 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean +INTMOMmean + Intdiff+  INTMOMdiff, data = data)
model.meanmomskids_11<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffmomsint_11 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff + Gendermean + INTMOMmean:Gendermean, data = data)
data=LinkedMDAN_discord_AFI_g_11

model.meankids.g_11<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.g_11<-lm(AFIKIDmean ~ INTMOMmean, data = data)
nested<-data
nested$Int_Mean[is.na(nested$Intdiff)] <- NA
model.diffkids.g_11<- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffkids.g.full_11 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = nested)
model.diffkids.g.nested_11 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean , data = nested)
anova_11<-anova(model.diffkids.g.nested_11,model.diffkids.g.full_11)
model.diffmoms.g_11<- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.g_11 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
model.meanmomskids.g_11<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
data=LinkedMDAN_discord_AFI_b_11
model.meankids.b_11<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.b_11<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.meanmomskids.b_11<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffkids.b_11 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms.b_11 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.b_11 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
@
<<setup_summarystats,include=FALSE>>=
#summarystats
birthweight <- read.table(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/79/SASGen1Kids/birthweight.dat",sep=""), quote="\"", stringsAsFactors=FALSE)
names(birthweight)<-c('CASEID','MCASEID','RACE','SEX_G2','YRB','WGT')
birthweight$WGT[birthweight$WGT < 0] <- NA
birthweight$firstborn<-0
birthweight$firstborn<-substrRight(birthweight$CASEID,2)
birthweight_2<-birthweight
birthweight$born[birthweight$firstborn!="01"]<-0
birthweight$born[birthweight$firstborn=="01"]<-1
birthweight_fb <- birthweight[ which(birthweight$born==1), ]

new_data <- read.table('gen2demographics.dat', sep=' ')
names(new_data) <- c('C0000100','C0000200','C0005300','C0005400')

# Handle missing values
  new_data[new_data == -1] = NA  # Refused 
  new_data[new_data == -2] = NA  # Dont know 
  new_data[new_data == -3] = NA  # Invalid missing 
  new_data[new_data == -7] = NA  # Missing

# If there are values not categorized they will be represented as NA
vallabels = function(data) {
 # data$C0000100 <- cut(data$C0000100, c(1.0,9999999.0), labels=c("1 TO 9999999: See Min & Max values below for range as of this release"), right=FALSE)
#  data$C0000200 <- cut(data$C0000200, c(1.0,12686.0), labels=c("1 TO 12686: NLSY79 Public ID"), right=FALSE)
  data$C0005300 <- factor(data$C0005300, levels=c(1.0,2.0,3.0), labels=c("Hispanic","Black","Non-Black, Non-Hispanic"))
  data$C0005400 <- factor(data$C0005400, levels=c(1.0,2.0), labels=c("Male","Female"))
  return(data)
}

varlabels <- c(    "ID CODE OF CHILD",
    "ID CODE OF MOTHER OF CHILD",
    "RACE OF CHILD (FROM MOTHERS SCREENER 79)",
    "SEX OF CHILD"
)

qnames = function(data) {
  names(data) <- c("CASEID","MCASEID","RACE","CSEX")
  return(data)
}

categories_g2 <- qnames(vallabels(new_data))

momintel <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/79/SASGen1/momintel.csv",sep=""), header=FALSE)
names(momintel)<-c("MCASEID","Intel_G1","Intel_G1_SE","HID")
#momintel$zIntel_G1<-scale(momintel$Intel_G1, center = TRUE, scale = TRUE)*15+100

kidintel<-read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/79/kidsintl/cleaned_CFA_G_around_910811.csv",sep=""), header=FALSE)
names(kidintel)<-c("CASEID","ASEID","Intel_G2","Intel_G2_SE","MCASEID")
#kidintel$zIntel_G2<-scale(kidintel$Intel_G2, center = TRUE, scale = TRUE)*15+100
Gen1AFI_exportconcor <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/Gen1AFI_exportconcor_910811.csv",sep=""))
Gen1AFI_exportconcor <- Gen1AFI_exportconcor[2:length(Gen1AFI_exportconcor[,1]),]
names(Gen1AFI_exportconcor)<-c("MCASEID","AFI_G1")
Gen2AFI_exportconcor <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/Gen2AFI_exportconcor_910811.csv",sep=""))
names(Gen2AFI_exportconcor)<-c("CASEID","AFI_G2")

Gen1AFIConcor <- merge(momintel,Gen1AFI_exportconcor,by="MCASEID",all=T)
Gen2AFIConcor <- merge(kidintel,Gen2AFI_exportconcor,by="CASEID",all=T)
Gen2AFIConcor_2 <- merge(categories_g2,Gen2AFI_exportconcor,by="CASEID",all=T)
@
<<setup_Reliability,include=FALSE>>=
##Reliability 
#AFI G1

new_data <- read.table('afi_reliability.dat', sep=' ')
names(new_data) <- c('R0000100','R0000149','R0214700','R0214800','R0988000','R1020700','R1312200','R1379600','R1379700','R1379800','R1691600','R1760000','R1760100','R1760200')

# Handle missing values
  new_data[new_data == -1] = NA  # Refused 
  new_data[new_data == -2] = NA  # Dont know 
  new_data[new_data == -3] = NA  # Invalid missing 
  new_data[new_data == -4] = NA  # Valid missing 
  new_data[new_data == -5] = NA  # Non-interview

# If there are values not categorized they will be represented as NA
vallabels = function(data) {
  data$R0214700 <- factor(data$R0214700, levels=c(1.0,2.0,3.0), labels=c("Hispanic","Black","Non-Black, Non-Hispanic"))
  data$R0214800 <- factor(data$R0214800, levels=c(1.0,2.0), labels=c("Male","Female"))
  return(data)
}

varlabels <- c(    "ID# (1-12686) 79",
    "HH ID # 79",
    "RACL/ETHNIC COHORT /SCRNR 79",
    "SEX OF R 79",
    "MALE AGE 1ST HAD INTERCOURSE 83",
    "F AGE 1ST HAD SEXUAL INTERCOURSE 83",
    "MALE AGE 1ST HAD INTERCOURSE 84",
    "F AGE 1ST HAD SEXUAL INTERCOURSE 84",
    "F USE B-DT YR 1ST INTERCOURSE 84",
    "F MO SEXUAL INTERCOURSE 1ST TIME 84",
    "MALE AGE 1ST HAD INTERCOURSE 85",
    "F AGE 1ST HAD SEXUAL INTERCOURSE 85",
    "F USE B-DT YR/1ST INTERCOURSE 85",
    "F MO SEXUAL INTERCOURSE 1ST TIME 85"
)

# Use qnames rather than rnums
qnames = function(data) {
  names(data) <- c("CASEID","HHID","RACE","SEX","MAFI_1983","FAFI_1983","MAFI_1984","FAFI_1984","FAFI_YEAR_1984","FAFI_MON_1984","MAFI_1985","FAFI_1985","FAFI_YEAR_1985","FAFI_MON_1985")
  return(data)
}

# Remove the '#' before the following line to create a data file called "categories" with value labels. 
categories <- vallabels(new_data)

# Remove the '#' before the following lines to rename variables using Qnames instead of Reference Numbers
categories <- qnames(categories)
testretest<-categories[,c(1,2,4)]
testretest$AFI_83<-as.numeric(NA);testretest$AFI_84<-as.numeric(NA);testretest$AFI_85<-as.numeric(NA);testretest$AFI_83z<-as.numeric(NA);testretest$AFI_84z<-as.numeric(NA);testretest$AFI_85z<-as.numeric(NA)
for(i in 1:length(categories[,1])){
  if(testretest$SEX[i]=="Male"){
    testretest$AFI_83[i]<-as.numeric(categories$MAFI_1983[i])
    testretest$AFI_84[i]<-as.numeric(categories$MAFI_1984[i])
    testretest$AFI_85[i]<-as.numeric(categories$MAFI_1985[i])
    testretest$AFI_83z[i]<-(as.numeric(categories$MAFI_1983[i])-15.88)/2.15
    testretest$AFI_84z[i]<-(as.numeric(categories$MAFI_1984[i])-15.88)/2.15
    testretest$AFI_85z[i]<-(as.numeric(categories$MAFI_1985[i])-15.88)/2.15
  }
    if(testretest$SEX[i]=="Female"){
    testretest$AFI_83[i]<-as.numeric(categories$FAFI_1983[i])
    testretest$AFI_84[i]<-as.numeric(categories$FAFI_1984[i])
    testretest$AFI_85[i]<-as.numeric(categories$FAFI_1985[i])
    testretest$AFI_83z[i]<-(as.numeric(categories$FAFI_1983[i])-16.47)/1.99
    testretest$AFI_84z[i]<-(as.numeric(categories$FAFI_1984[i])-16.47)/1.99
    testretest$AFI_85z[i]<-(as.numeric(categories$FAFI_1985[i])-16.47)/1.99
    }
}
names(momintel)<-c("CASEID","Intel_G1","Intel_G1_SE","HID") 
testretest<-merge(testretest,momintel[c(1,2)],by="CASEID", all=T)

library(NlsyLinks)
dsLinking <- subset(Links79Pair, RelationshipPath=="Gen1Housemates")

dsOutcomes <- testretest
dsOutcomes$SubjectTag <-dsOutcomes$CASEID*100
dsSingle <- CreatePairLinksSingleEntered(
outcomeDataset = dsOutcomes,
linksPairDataset = dsLinking,
outcomeNames = c(
"AFI_83","AFI_84","AFI_85","AFI_83z","AFI_84z","AFI_85z"
)
)

dsD <- CreatePairLinksDoubleEntered(
outcomeDataset = dsOutcomes,
linksPairDataset = dsLinking,
outcomeNames = c(
"AFI_83","AFI_84","AFI_85","AFI_83z","AFI_84z","AFI_85z","Intel_G1","SEX"
)
)
dsD_nm<-dsD[dsD$SEX_S1=="FEMALE"]
dsSingle$DIF_AFI_83z<-dsSingle$AFI_83z_S1-dsSingle$AFI_83z_S2
dsSingle$DIF_AFI_84z<-dsSingle$AFI_84z_S1-dsSingle$AFI_84z_S2
dsSingle$DIF_AFI_85z<-dsSingle$AFI_85z_S1-dsSingle$AFI_85z_S2
matrix_g1<-data.frame(dsD$Intel_G1_S1,dsD$Intel_G1_S2)

matrix_afi_diff<-data.frame(dsSingle$DIF_AFI_83z,dsSingle$DIF_AFI_84z,dsSingle$DIF_AFI_85z)
names(matrix_afi_diff)<-c("1983","1984","1985")
capture.output(xtable(cor_1star(matrix_afi_diff,2,.01,include.n=TRUE)),file="content/table/table_diffafireliable_z.tex")
matrix_tt_z<-data.frame(dsD$AFI_83z_S1,dsD$AFI_84z_S1,dsD$AFI_85z_S1)
#matrix_tt<-data.frame(dsD$AFI_83_S1,dsD$AFI_84_S1,dsD$AFI_85_S1)
#matrix_tt[matrix_tt<12]<-NA
names(matrix_tt_z)<-c("1983","1984","1985")
#names(matrix_tt)<-c("1983","1984","1985")
capture.output(xtable(cor_1star(matrix_tt_z,2,.01,include.n=TRUE)),file="content/table/table_ttafireliable_z.tex")
capture.output(xtable(cor_1star(matrix_g1,2,.01,include.n=TRUE)),file="content/table/table_sibintreliable_z.tex")
#capture.output(xtable(cor_1star(matrix_tt,2,.01,include.n=TRUE)),file="content/table/table_ttafireliable.tex")

#AFI g2

dsLinking <- subset(Links79Pair, RelationshipPath=="Gen1Housemates")
total_data <- read.csv("C:/Dropbox/Work/Research/Projects/NLSY/AFI/R/gen2demographics.csv", stringsAsFactors=FALSE)
dsOutcomes <- data.frame(Gen2AFIConcor,total_data$CSEX)

dsOutcomes$AFI_G2z<-as.numeric(NA)
mean_s1<-mean(dsOutcomes$AFI_G2[dsOutcomes$total_data.CSEX==1],na.rm=TRUE)
mean_s2<-mean(dsOutcomes$AFI_G2[dsOutcomes$total_data.CSEX==2],na.rm=TRUE)

sd_s1<- sd(dsOutcomes$AFI_G2[dsOutcomes$total_data.CSEX==1],na.rm=TRUE)
sd_s2<-sd(dsOutcomes$AFI_G2[dsOutcomes$total_data.CSEX==2],na.rm=TRUE)
dsOutcomes<-merge(dsOutcomes[c(1,2,6,8)],birthweight_fb, by="CASEID")
for(i in 1:nrow(dsOutcomes)){
  if(dsOutcomes$SEX_G2[i]==2&!is.na(dsOutcomes$SEX_G2[i])
){
    dsOutcomes$AFI_G2z[i]<- (dsOutcomes$AFI_G2[i]-mean_s2)/sd_s2
  }
  if(dsOutcomes$SEX_G2[i]==1&!is.na(dsOutcomes$SEX_G2[i])
){
    dsOutcomes$AFI_G2z[i]<- (dsOutcomes$AFI_G2[i]-mean_s1)/sd_s1
  }
}
dsOutcomes$SubjectTag<-dsOutcomes$MCASEID*100

dsSinglez <- CreatePairLinksSingleEntered(
outcomeDataset = dsOutcomes,
linksPairDataset = dsLinking,
outcomeNames = c(
"AFI_G2","AFI_G2z","SEX_G2")
)

dsDz <- CreatePairLinksDoubleEntered(
outcomeDataset = dsOutcomes,
linksPairDataset = dsLinking,
outcomeNames = c(
"AFI_G2","AFI_G2z","SEX_G2")
)

matrix_afi_cousincor<-data.frame(dsSinglez$AFI_G2z_S1,dsSinglez$AFI_G2z_S2)

capture.output(xtable(cor_1star(matrix_afi_cousincor,2,.01,include.n=TRUE)),file="content/table/table_sibafig2_z.tex")
Cor(matrix_afi_cousincor)
#INTEL
G_G2_9.5 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/79/kidsintl/cleaned_CFA_G_around_910811.csv",sep=""), header=FALSE)
names(G_G2_9.5)<-c("CASEID","ASEID","G_G2_9.5","G_SE_G2_9.5","MCASEID")
G_G2_10.5 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/79/kidsintl/cleaned_CFA_G_around_1011912.csv",sep=""), header=FALSE)
names(G_G2_10.5)<-c("CASEID","ASEID","G_G2_10.5","G_SE_G2_10.5","MCASEID")
G_G2_11.5 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/79/kidsintl/cleaned_CFA_G_around_11121013.csv",sep=""), header=FALSE)
names(G_G2_11.5)<-c("CASEID","ASEID","G_G2_11.5","G_SE_G2_11.5","MCASEID")
temp<-merge(G_G2_9.5[c(1,3)],G_G2_10.5[c(1,3)],by="CASEID",all=T)
G_G2<-merge(temp,G_G2_11.5[c(1,3)],by="CASEID",all=T)
capture.output(xtable(cor_1star(G_G2[2:4],2,.01,include.n=TRUE)),file="content/table/table_ttintreliable_z.tex")
#standardized gendermxedd
LinkedMDAN_discord_AFI_z_9_m<-LinkedMDAN_discord_AFI_z_9[,c(2,56,66,68,70,72,90)]
names(LinkedMDAN_discord_AFI_z_9_m) <-c("ID" ,"AFIMOMdiff_9", "INTMOMdiff_9","AFMKIDdiff_9","AFIKIDdiff_9","CSMOMdiff_9",  "Intdiff_9" ) 
LinkedMDAN_discord_AFI_z_10_m<-LinkedMDAN_discord_AFI_z_10[,c(2,56,66,68,70,72,90)]
names(LinkedMDAN_discord_AFI_z_10_m) <-c("ID" ,"AFIMOMdiff_10", "INTMOMdiff_10","AFMKIDdiff_10","AFIKIDdiff_10","CSMOMdiff_10",  "Intdiff_10" ) 
LinkedMDAN_discord_AFI_z_11_m<-LinkedMDAN_discord_AFI_z_11[,c(2,56,66,68,70,72,90)]
names(LinkedMDAN_discord_AFI_z_11_m) <-c("ID" ,"AFIMOMdiff_11", "INTMOMdiff_11","AFMKIDdiff_11","AFIKIDdiff_11","CSMOMdiff_11",  "Intdiff_11" ) 
diffscorereliable_z <- merge(LinkedMDAN_discord_AFI_z_9_m,LinkedMDAN_discord_AFI_z_10_m,by="ID",all=T)
diffscorereliable_z <- merge(diffscorereliable_z,LinkedMDAN_discord_AFI_z_11_m,by="ID",all=T)
matrix_z<-data.frame(diffscorereliable_z$Intdiff_9,diffscorereliable_z$Intdiff_10,diffscorereliable_z$Intdiff_11)
names(matrix_z)<-c("Age 9.5","Age 10.5","Age 11.5")
#Girls
LinkedMDAN_discord_AFI_g_9_m<-LinkedMDAN_discord_AFI_g_9[,c(2,57,67,69,71,73,92)]
names(LinkedMDAN_discord_AFI_g_9_m) <-c("ID" ,"AFIMOMdiff_9", "INTMOMdiff_9","AFMKIDdiff_9","AFIKIDdiff_9","CSMOMdiff_9",  "Intdiff_9" ) 
LinkedMDAN_discord_AFI_g_10_m<-LinkedMDAN_discord_AFI_g_10[,c(2,57,67,69,71,73,92)]
names(LinkedMDAN_discord_AFI_g_10_m) <-c("ID" ,"AFIMOMdiff_10", "INTMOMdiff_10","AFMKIDdiff_10","AFIKIDdiff_10","CSMOMdiff_10",  "Intdiff_10" ) 
LinkedMDAN_discord_AFI_g_11_m<-LinkedMDAN_discord_AFI_g_11[,c(2,57,67,69,71,73,92)]
names(LinkedMDAN_discord_AFI_g_11_m) <-c("ID" ,"AFIMOMdiff_11", "INTMOMdiff_11","AFMKIDdiff_11","AFIKIDdiff_11","CSMOMdiff_11",  "Intdiff_11" ) 
diffscorereliable_g <- merge(LinkedMDAN_discord_AFI_g_9_m,LinkedMDAN_discord_AFI_g_10_m,by="ID",all=T)
diffscorereliable_g <- merge(diffscorereliable_g,LinkedMDAN_discord_AFI_g_11_m,by="ID",all=T)
matrix_g<-data.frame(diffscorereliable_g$Intdiff_9,diffscorereliable_g$Intdiff_10,diffscorereliable_g$Intdiff_11)
names(matrix_g)<-c("Age 9.5","Age 10.5","Age 11.5")

>>>>

\documentclass[a4paper,man,apacite,natbib,12pt]{apa6}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
%%%%%%%%%%%% Packages %%%%%%%%%%%%
%%% Formatting
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{verbatim}
\usepackage[yyyymmdd,hhmmss]{datetime}

@@

\authornote{This material is based upon work that has been supported by National Institute of Health under Grant No. (R01-HD065865) and the National Science Foundation Graduate Research Fellowship Program under Grant No. (DGE-1445197) and various means of institutional support from the following universities: University of British Columbia, University of Oklahoma \& Vanderbilt University.}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\maketitle
%\linenumbers%\section{Introduction}\section{ }\vspace{-.8cm}
\input{content/introduction.txt}

@@

\section{Methods}\input{content/methods.txt}

\input{content/Gen1measure.txt}
